Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-03 ch04-lrmhinf/paper.tex
Improve intro Ch04

  \begin{itemize}
    \item \TODO{add section from Benchmark paper}
    \item \TODO{Hinf macro aanpassen voor PDF support (indien dit niet conflicteert met glossaries)}
    \item \TODO{refer to book chapter of Tom}
  \end{itemize}

\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
\newcommand{\dampingValue}{\ensuremath{0.025}}
\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}

@@

@@

\paragraph*{Direct method}
% \subsubsection{Direct method}
One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gammaIntergrid$ directly.
Hence, it boils down to solving the optimization problems
\begin{align}
  \estimated{\gammaIntergrid}(k) & \isdef 
      \sup_{\omega \in \Omega_k}
      \svdMax{\LocalModel{\Delta}_k(\omega)}
       \quad \forall k \in \Set{1,\ldots,N-1} \\
  \estimated {\gammaIntergrid} &= 
  \max \Set{
    \estimated{\gammaIntergrid}(k) 
    | 
    k \in \Set{1,\ldots,N-1}
  }
      \label{eq:lrmhinf:gamma-direct}
\end{align}
These are tractable since $\omega$ is one-dimensional and restricted to the closed intervals $\Omega_k$.
Unfortunately, this approach offers no insight in the behavior of $\svdMax{\Delta(\omega)}$, e.g. around the peak amplitude.

\paragraph{Interpolation method}
To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\svdMax{\omega_k-\omega}$ is small.
To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
\begin{align}
  k_L(\omega) & 
                \isdef
                  \max
                  \Set{
                    k 
                    |
                      \omega_k \in \DFTGrid,  \omega_k \leq \omega
                  }\\
  k_R(\omega) & 
                \isdef
                  \min
                  \Set{
                    k
                    |
                      \omega_k \in \DFTGrid,  \omega_k \geq \omega
                  }
  \text{.}
  \label{eq:lrmhinf:kL-kR-indexing-functions}
\end{align}
Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained: $\svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$ and $\svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
\begin{equation}
  \svdMax{\Delta_{\LMM}(\omega)}
    \isdef
    \sup \Set{
       \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
        \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
    }
    \label{eq:lrmhinf:DeltaLRMInterpolation}
\end{equation}
by retaining the largest both.
It follows that
\begin{align}
  \widehat{\infnorm{\Delta_{\LMM}}}
    & \isdef
    \sup_{\omega\in\Omega}
    \svdMax{\Delta_{\LMM}(\omega)} \\
   &  =
      \sup_{\omega\in\Omega} \; 
      \sup \Set{
                 \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
                 \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
  \label{eq:lrmhinf:gammaInterpolOptim}
  \text{.}
\end{align}

>>>>

  \begin{itemize}
    \item \TODO{add section from Benchmark paper}
  \end{itemize}
\newcommand{\wnValue}{\ensuremath{0.95 \unit{rad/s}}}
\newcommand{\dampingValue}{\ensuremath{0.025}}
\newcommand{\TsValue}{\ensuremath{1 \unit{s}}}

@@

For mechatronic design and many other engineering disciplines it is important to obtain good parametric models.
However, in many state-of-the-art disciplines that involve increasingly complicated systems, building a full-scale model quickly becomes a burden that is not guaranteed to provide a level of model fidelity that is proportional to the required modeling effort and cost.
Often, such parametric models are required to understand basic properties of the system such as the resonance frequencies and their corresponding damping values.
In this chapter, we will investigate the use of the local parametric approaches to extract such basic information from the system without having to build a full parametric model.
The approach that is followed in this chapter is applied to estimating the \Hinf{} norm of the transfer function of a system, a problem that directly depends on the resonances of system and has shown to be a crucial step in designing robust controllers~\citep{Oomen2016}.

@@

\paragraph*{Direct method}
One can implement the definition~\eqref{eq:lrmhinf:gamma-inter-grid} of $\gammaIntergrid$ directly.
Hence, it boils down to solving the optimization problems
\begin{align}
  \estimated{\gammaIntergrid}(k) & \isdef 
      \sup_{\omega \in \Omega_k}
      \svdMax{\LocalModel{\Delta}_k(\omega)}
       \quad \forall k \in \Set{1,\ldots,N-1} \\
  \estimated {\gammaIntergrid} &= 
  \max \Set{
    \estimated{\gammaIntergrid}(k) 
    | 
    k \in \Set{1,\ldots,N-1}
  }
      \label{eq:lrmhinf:gamma-direct}
\end{align}
These are tractable since $\omega$ is one-dimensional and restricted to the closed intervals $\Omega_k$.
Unfortunately, this approach offers no insight in the behavior of $\svdMax{\Delta(\omega)}$, e.g. around the peak amplitude.

\paragraph{Interpolation method}
To allow inspection of $\svdMax{\Delta(\omega)}$ in~\eqref{eq:lrmhinf:HinfNormSISO} for arbitrary values of $\omega \in \Omega$, we propose an interpolation approach to estimate $\gamma$ and to allow visual inspection of $\svdMax{\Delta(\omega)}$.
It can be understood intuitively that due to the limited validity domain of the local models, an estimate of $\Delta(\omega)$ can only be obtained from $\LocalModel{\Delta}_k(\omega)$ when $\svdMax{\omega_k-\omega}$ is small.
To this end, two functions that indicate respectively the left and the right adjacent local models for frequency $\omega \in \Omega$ are defined:
\begin{align}
  k_L(\omega) & 
                \isdef
                  \max
                  \Set{
                    k 
                    |
                      \omega_k \in \DFTGrid,  \omega_k \leq \omega
                  }\\
  k_R(\omega) & 
                \isdef
                  \min
                  \Set{
                    k
                    |
                      \omega_k \in \DFTGrid,  \omega_k \geq \omega
                  }
  \text{.}
  \label{eq:lrmhinf:kL-kR-indexing-functions}
\end{align}
Using the $k_L(\omega)$ and $k_R(\omega)$ functions, two candidate values for $\svdMax{\Delta(\omega)}$ are obtained:
\begin{itemize}
 \item $\svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}$, and 
 \item $\svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}$.
\end{itemize}
In view of obtaining the maximum singular value, these are `interpolated' to obtain a single estimate:
\begin{equation}
  \svdMax{\Delta_{\LMM}(\omega)}
    \isdef
    \max \Set{
       \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)},
        \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}
    }
    \label{eq:lrmhinf:DeltaLRMInterpolation}
\end{equation}
by retaining the largest both.
It follows that
\begin{align}
  \widehat{\infnorm{\Delta_{\LMM}}}
    & \isdef
    \sup_{\omega\in\Omega}
    \svdMax{\Delta_{\LMM}(\omega)} \\
   &  =
      \sup_{\omega\in\Omega} \; 
      \max \Set{
                 \svdMax{\LocalModel{\Delta}_{k_L(\omega)}(\omega)}, 
                 \svdMax{\LocalModel{\Delta}_{k_R(\omega)}(\omega)}}
  \label{eq:lrmhinf:gammaInterpolOptim}
  \text{.}
\end{align}
